---
title: "Fox Lab Intro to R 2023"
author: "Alicia Vallorani"
date: "2023-09-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview
This document is designed to provide an introduction to using R for basic data
manipulation, visualization and analyses. This document assumes the user knows
the basics of R and RStudio. For more information about setting-up R, please see
https://github.com/auv27/intro_to_r/tree/main/getting_started.

This document is known as an RMarkdown. RMarkdown is a useful tool for 
integrating text and code. It is also possible to use basic r scripts to conduct
any processes shown here.


# Loading packages
The code I am including here will automatically install and load packages that 
are needed for the script to run. Some people don't like this and prefer the
choice of what to install so just be cognizant. If you do not want to install 
everything, you can use `install.packages()` to install individual packages and
`library()` to load individual packages.

In the call below, I load tidyverse which is a package containing a family of 
packages (see the following website to learn more about tidyverse 
https://www.tidyverse.org/). For this script, I am using the following tidyverse
packages: tidyr, dplyr, ggplot2. I will also use the psych and Hmisc packages.
```{r}
if (!("pacman" %in% installed.packages()[,])) {
    install.packages("pacman")
  }
pacman::p_load(tidyverse, psych, Hmisc)
```


# Setting up an environment
There are a few different ways to set-up an environment for manipulating,
analyzing and visualizing data in R. Some people like to use "projects" (see
the following website for information about projects in RStudio https://bookdown.org/daniel_dauber_io/r4np_book/starting-your-r-projects.html).
Others prefer to use the setwd() function to specify a path that R should refer
to for all processes (see the following website for an explanation https://finnstats.com/2021/12/30/get-and-set-working-directory-setwd-getwd-in-r/).
I prefer to use relative paths because of the flexibility it affords, but there
is not right or wrong way to set-up an environment. Just choose what works best
for you.
```{r}
# Set home path for the session 
home_path <- "/Users/aliciavallorani/Library/CloudStorage/Box-Box/Standard Codes/intro_to_r"
```

